\newcommand{\checkedBox}{\makebox[0pt][l]{$\square$}\raisebox{.15ex}{\hspace{0.1em}$\checkmark$}}
\newcommand{\uncheckedBox}{\makebox[0pt][l]{$\square$}\raisebox{.15ex}{\hspace{0.1em}\phantom{$\checkmark$}}}

\section{Proposed Timeline}

\begin{itemize}
 \item May 8th through May 21st:
       \begin{itemize}
        \item [\uncheckedBox] Create a GitHub repository for the project.
        \item [\uncheckedBox] Design a template for binned models that is parametrized in terms of number of events, number of bins, number of channels, number of signal/background components, and number of parameters of interest and nuisance parameters.
        \item [\uncheckedBox] Begin documentation of the template model on the GitHub repository.
       \end{itemize}
 \item May 22nd through June 4th:
       \begin{itemize}
        \item [\uncheckedBox] Establish a precise mathematical formulation that is implementation-independent based on the \code{HistFactory} schema.
        \item [\uncheckedBox] Begin study of data flow graph frameworks or of probabilistic programming frameworks.
        \item [\uncheckedBox] Implement the template for the benchmark models with a \code{HistFactory} script.
       \end{itemize}
 \item June 5th through June 18th:
       \begin{itemize}
        \item [\uncheckedBox] Conclude from study of data flow graph frameworks or of probabilistic programming frameworks which framework to pursue.
        \item [\uncheckedBox] Begin implementation of the benchmark models in the selected framework.
        \item [\uncheckedBox] Begin to write technical report.
       \end{itemize}
 \item June 19th through July 2nd:
       \begin{itemize}
        \item [\uncheckedBox] Finish implementation of the benchmark models in the selected framework.
        \item [\uncheckedBox] Apply benchmarks evaluating framework data and model parallelism.
       \end{itemize}
 \item July 3rd through July 16th:
       \begin{itemize}
        \item [\uncheckedBox] Finish technical report.
        \item [\uncheckedBox] Create tutorial on data flow graphs targeted for physicists.
       \end{itemize}
 \item July 17th through August 8th:
       \begin{itemize}
        \item [\uncheckedBox] Upstream software contributions to address the identified limitations (if any).
        \item [\uncheckedBox] Development of/Contribution to a probabilistic framework (if time permits).
       \end{itemize}
\end{itemize}
